Cooperation Provably Prevails in a Version of the Noisy Iterated Prisoner's Dilemma

### 2020-05-06 paper/paper.tex
rename to paper again
add title
change title

\title{Prisoner's Dilemma}
\author{Arvid Lunnemark. \\ \\
Supervised by: Michael Sipser}

@@

\begin{lemma}
  \label{payofftimeaverage}
  The payoff when $s_1$ plays against $s_2$ is
  \begin{equation*}
    v_{s_1}(s_2) = \sum_{(c_1,c_2) \in S_{s_1,s_2}} \pi_{c_1,c_2}^{(c_{\text{start}}(s_1), c_{\text{start}}(s_2))} \cdot r(c_1,c_2).
  \end{equation*}
\end{lemma}

We may also make $r(c_1,c_2)$ into a vector, denoted by $r$, and write this as \begin{equation*}
  v_{s_1}(s_2) = \pi^{(c_{\text{start}}(s_1), c_{\text{start}}(s_2))} \cdot r.
\end{equation*}

@@

      We will first finish the proof of the theorem assuming this claim, and then prove it.

>>>>

\title{Cooperation Provably Prevails in a Version of the Noisy Iterated Prisoner's Dilemma}
\author{Arvid Lunnemark. \\ \\
Supervised by: Michael Sipser}

@@

\begin{lemma}
  \label{payofftimeaverage}
  The payoff when $s_1$ plays against $s_2$ is
  \begin{equation*}
    v_{s_1}(s_2) = \sum_{(c_1,c_2) \in S_{s_1,s_2}} \pi_{c_1,c_2}^{(c_{\text{start}}(s_1), c_{\text{start}}(s_2))} \cdot r(G_{s_1}(c_1),G_{s_2}(c_2)).
  \end{equation*}
\end{lemma}

We may also make $r(G_{s_1}(c_1),G_{s_2}(c_2))$ into a vector, denoted by $r$, and write this as \begin{equation*}
  v_{s_1}(s_2) = \pi^{(c_{\text{start}}(s_1), c_{\text{start}}(s_2))} \cdot r.
\end{equation*}

@@

      Before proving this claim, we will use it to finish our proof of \cref{evolutionarystable1}.
